---
title: "Confidence Intervals for Percentiles"
author: "Eamonn"
date: '`r format(Sys.time(), "%d %B, %Y")`'
header-includes:
- \usepackage{eso-pic,graphicx,transparent}
- \usepackage{graphicx}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \setlength\headheight{22pt}
- \fancyfoot[RO]{Data Management}
- \usepackage{lastpage}
- \cfoot{Page \thepage\ of \pageref{LastPage}}
output:
  pdf_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 8
    number_sections: no
  html_document: default
  word_document: default
---
 
 
\AddToShipoutPictureFG{
  \AtPageCenter{% or \AtTextCenter
    \makebox[0pt]{\rotatebox[origin=c]{45}{%
      \scalebox{5}{\texttransparent{0.3}{  }}%
    }}
  }
}
 
 
 
```{r set-options, echo=FALSE, cache=FALSE, warning = FALSE}
 
        rm(list=ls())
 
        set.seed(123)
        startTime<-proc.time()
        library(knitr)
        options(width=70)
        opts_chunk$set(comment = "", warning = FALSE, message = FALSE,
                       echo = FALSE, tidy = FALSE, size="tiny",  cache=FALSE,
                       progress=TRUE,
                       cache.path = 'program_Cache/',
                       fig.path='figure/')
         
        knitr::knit_hooks$set(inline = function(x) {
          knitr:::format_sci(x, 'md')
        })
         
        
```
 
<!-- \begin{figure}[t!] -->
<!--   \centering -->
<!--     \includegraphics[keepaspectratio, width=0.2\textwidth]{LOGO.png} -->
<!--   \label{fig:RSUencountered} -->
<!-- \end{figure} -->
 
 
 
 
```{r prerequisites, echo=FALSE}

        where<-"home"
        x  <- "Users\\User\\Documents\\GIT"
        
        path <- paste(x,"\\confidence-intervals-for-percentilers",sep="")
        path2 <- paste(x,"\\DATA",sep="")
        
        work<-    paste("C:/", path, sep = "")
        nonwork<- paste("C:/", path, sep = "")
        if (where=="home") {wd<- nonwork} else {wd<-work}
        
        work2<-    paste("X:/", path2, sep = "")
        nonwork2<- paste("~/X/", path2, sep = "")
        if (where=="home") {wd2<- nonwork2} else {wd2<-work2}
        
        work3<-    paste("X:/FUNCTIONS/R", sep = "")
        nonwork3<- paste("~/X/FUNCTIONS/R", sep = "")
        if (where=="home") {wd3<- nonwork3} else {wd3<-work3}
        
        setwd(wd)
        opts_knit$set(root.dir = wd)  # THIS SETS YOUR WORKING DIRECTORY
        
```
```{r preliminaries perhaps , echo=FALSE, results='hide'}
 
        p3 <- function(x) {formatC(x, format="f", digits=3)}
        p4 <- function(x) {formatC(x, format="f", digits=4)}
        p2 <- function(x) {formatC(x, format="f", digits=2)}
        p1 <- function(x) {print(formatC(x, format="f", digits=1),quote=FALSE)}
        
        # perhaps help colour plot text based on loop count
        is.even <- function(x){ x %% 2 == 0 }
 
        # Load relevant packages
        list.of.packages <- c("DescTools","boot")
 
        new.packages <- 
                list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
        if(length(new.packages)) install.packages(new.packages)
        
        sapply(X = list.of.packages, require, character.only = TRUE)
        
```
 
# Quantiles of the binomial distribution approach
 
```{r quantile, echo=TRUE, results='markdown' }
      
      set.seed(321)
      x <- rexp(120, rate=0.10) # create continuous data, no ties

      conf2 <- 0.95             # confidence level
      low <- (1- conf2)/2 ; up <- 1-low
      
      # What percentile is the value of 10? 
      (p <- sum(x <= 1/0.10 )/length(x))  
      
      # confidence intervals for the percentile estimate 'p'
      sort(x)[qbinom(c(low, up), size=length(x), prob=p)]
       
```
 
# Bootstrap method (BCa), an approximation to the quantiles of the binomial distribution approach
 
```{r boot, echo=TRUE, results='markdown' }

      f.quantile <- function(x, ind, ...){ 
        quantile(x[ind], ...) 
      } 
      
      # the percentile p is bootstrapped, ensure No of bootstraps is > than sample size
      quant.boot <- boot(x, f.quantile, R = 10000, probs = p)
      
      # apply the boo.ci function, note BCa option
      boot.ci(quant.boot, c(conf2), type = c("bca") )

```

# CONCLUSION
 
# REFERENCES

http://stats.stackexchange.com/questions/186957/ is-there-a-reliable-nonparametric-confidence-interval-for-the-mean-of-a-skewed-d
 
http://stats.stackexchange.com/questions/21103/confidence-interval-for-median/21116#21116

# COMPUTING ENVIRONMENT
 
```{r, echo=FALSE}
options(width=70)
opts_knit$set(root.dir = wd)   ##THIS SETS YOUR WORKING DIRECTORY
sessionInfo()
print(wd)
```
 
```{r echo=FALSE}
 
stopTime<-proc.time()
 
```
 
This took `r (stopTime-startTime)[1][[1]]` seconds to execute.

 
    
      
 
